Using a Highly Dynamic Language for Development

### 2021-10-09 gic2021-highly-dynamic/paper.tex
Minor

\begin{abstract}
  Games face an interesting challenge. They require rapid development, are highly interactive, and pose hard real-time performance constraints. While smaller games these days have also been developed in dynamic languages such as Python or Lua, traditionally engines are still written in static languages like C++ and C, with an additional scripting languages on top to handle gameplay mechanics. Common Lisp offers an environment that's both dynamic and performant enough to allow for a full stack game development system that is highly favourable to fast iteration and modular design.
\end{abstract}
\begin{keywords}
  Common Lisp, game development, dynamic languages, object orientation
\end{keywords}

>>>>

\begin{abstract}
  Games face an interesting challenge. They require rapid development, are highly interactive, and pose hard real-time performance constraints. While smaller games these days have also been developed in dynamic languages such as Python or Lua, traditionally engines are still written in static languages like C++ and C, with an additional scripting language on top to handle gameplay mechanics. Common Lisp offers an environment that's both dynamic and performant enough to allow for a full stack game development system that is highly favourable to fast iteration and modular design.
\end{abstract}
\begin{keywords}
  Common Lisp, game development, dynamic languages, object orientation
\end{keywords}
